\documentclass[11pt,twocolumn]{article}
\usepackage{color}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{layouts}
\usepackage{array}
\usepackage{tikz}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{lmodern}
\usepackage{epstopdf}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{bm}
\usepackage{enumerate}
\usepackage{url}
\usepackage{textcomp}
\usepackage{caption}

\hypersetup{
  colorlinks,%
    citecolor=red,%
    filecolor=red,%
    linkcolor=red,%
    urlcolor=blue     % can put red here to visualize the links
}

\title{Computer Vision\\ICP, EGC, SFM}
\author{Georgios Methenitis, Marios Tzakris, Paris Mavromoustakos}
\affil{University of Amsterdam}
\date{June 2014}

\begin{document}

\maketitle

\renewcommand{\labelenumi}{\alph{enumi}.}



\textbf{\textit{Abstract}- In this technical report we are presenting implementation details along with experimental results obtained for two separate classes of algorithms. We will discuss the Iterative Closest Point (ICP) algorithm and how variations in different parameters of the implementation affect its performance. In addition, this report addresses the Structure from Motion algorithm. We will show how 3D structure of a scene can be obtained from 2D images taken from multiple viewpoints.}


\section{Introduction}
\label{introduction}
Iterative Closest Point (ICP) as first described in~\cite{icp} is an alignment algorithm used to iteratively estimate the closest match between points in two point clouds or surface meshes. Section~\ref{icp} discusses the details of this procedure tested on a given dataset of point clouds representing a human, viewed from various camera positions. In addition, a variety of modifications of the algorithm are analyzed in terms of speed, accuracy, stability and tolerance to noise.
Furthermore, section~\ref{egc} and ~\ref{sfm} describe the Structure from Motion algorithm (SFM)~\cite{egc}. SFM is a process of estimating shape and motion parameters of a 3D scene from 2D images depicting the scene from multiple views. In particular Section~\ref{egc} addresses the task of computing the intrinsic projective (epipolar) geometry between two views and obtaining the global camera poses by chaining the derived geometrical measurements pairwise, while in Section~\ref{sfm} the method of extracting 3D structure of the scene given the chaining results, is explained.




\input{icp.tex}
\input{egc.tex}
\input{sfm.tex}




\section{Conclusion}

This lab assignment has been an educational and challenging task. We were able to observe how algorithm implementations work in practice by visualizing the results, and see how variations of these methods affect the constructed models.

We have realised that 3D model reconstruction is a computationally expensive and complex procedure, however, choice of the correct features, descriptors and point sampling methods can result to an efficient algorithm. 
\label{conclusion}


\begin{thebibliography}{9}

\bibitem{amb}
Toshihiko Morita and Takeo Kanade, ``A Sequential Factorization Method for Recovering Shape and Motion From Image Streams'', Fellow, IEEE, 1997.

\bibitem{pcl}
Radu Bogdan Rusu and Steve Cousins, ``3D is here: Point Cloud Library (PCL)'', IEEE International Conference on Robotics and Automation (ICRA), May 9-13 2011.

%\bibitem{myc}
%Luigi Giaccari, MyCrust.m toolbox,
%``http://www.codeforge.com/read/218867/MyCrust.m__html''

\bibitem{icp}
Besl, Paul J., and Neil D. McKay. ``Method for registration of 3-D shapes.'' In Robotics-DL tentative, pp. 586-606. International Society for Optics and Photonics, 1992.

\bibitem{egc}
Rothganger, Fred, Svetlana Lazebnik, Cordelia Schmid, and Jean Ponce. ``3d object modeling and recognition using local affine-invariant image descriptors and multi-view spatial constraints.'' International Journal of Computer Vision 66, no. 3 (2006): 231-259.

\bibitem{eight-point}
Richard I. Hartley. ``In Defence of the 8-point Algorithm.'' (1997)


\end{thebibliography}

\end{document}
